Proposed Solution

### 2016-11-12 Ennan-Proposal/motivation.tex
config: motiv

Configuration errors are one of the most important root causes of
today's software system failures~\cite{xu15systems, yin11anempirical}.
We read in the news that recently there was a problem in accessing  Facebook and Instagram \cite{mashableNews} and a Facebook spokeswoman that this was due to a change to the site's configuration systems.
While program verification is mostly focused on detecting errors 
in code, in their empirical study Yin {\em et al.}~\cite{yin11anempirical} report
that about 31\% of system failures were caused by configuration errors problems and only 20\% were caused by bugs in program code. Configuration 
errors are commonly known in literature under the name misconfigurations.

@@

We start by presenting two non-trivial configuration errors
extracted from real-world examples. Although the errors are relatively simple, we call them 
non-trivial, because the majority of existing tools, \eg, learning-based checking
tools~\cite{zhang14encore, wang04automatic}, cannot detect
these configuration errors. Most of the presented examples were found on StackOverflow,
a popular question and answer website for programmers.

@@

We believe there are two main obstacles 
why we cannot simply apply the existing automatic 
tools and techniques to verification of configuration files are:
\begin{itemize}
\item a lack
of a specification which would describe properties of configuration files
\item a program structure of configuration files -- they
are mainly a sequence of entries assigning some value to system keywords. 
\end{itemize}
The language in which configuration files are written does 
not adhere to a specific grammar or syntax. In particular, the
entries in configuration files are untyped. Moreover, there are surprisingly few rules specifying constraints on entries and there
is no explicit structure policy for the entries.
We believe that those are the reasons why there is no automated verification of configuration 
files although the system community expressed that that would be highly
desirable~\cite{wang04automatic, zhang14encore, xu15systems}.

>>>>

Configuration errors are one of the most important root causes of
today's software system failures~\cite{xu15systems, yin11anempirical}.
We read in the news that recently there was a problem in accessing  
Facebook and Instagram~\cite{mashableNews}, 
and a Facebook spokeswoman reported that 
this was caused by a change to the site's configuration systems.
In a recent software system failures study~\cite{yin11anempirical},
researchers revealed that about 31\% of system failures were caused by 
configuration errors, which is higher than the percentage of
failures resulting from program bugs (20\%). 
%(which and only 20\% were caused by bugs in program code 
%While program verification is mostly focused on detecting errors 
%in code, in their empirical study 
%Yin {\em et al.}~\cite{yin11anempirical} report
%that about 31\% of system failures were caused by configuration errors problems and only 20\% were caused by bugs in program code. 
Configuration errors are commonly known in literature 
under the name misconfigurations.

@@

We start by presenting two non-trivial configuration errors
extracted from real-world examples. 
Although the errors are relatively simple, we call them 
non-trivial, because the majority of existing misconfiguration
checking tools~\cite{zhang14encore, wang04automatic} cannot detect
these configuration errors. 
Most of the presented examples were found on
StackOverflow~\cite{stackoverflow},
a popular Q\&A website for programmers.

@@

We believe there are two main obstacles 
why we cannot simply apply the existing automatic 
tools and techniques to verification of configuration files are:
\begin{itemize}
\item a lack
of a specification describing properties of configuration files
\item a program structure of configuration files -- they
are mainly a sequence of entries assigning some value to system
variables (called {\emph {keywords}}). 
\end{itemize}
The language in which configuration files are written does 
not adhere to a specific grammar or syntax. In particular, the
entries in configuration files are untyped. Moreover, there are surprisingly few rules specifying constraints on entries and there
is no explicit structure policy for the entries.
We believe that those are the reasons why there is no automated verification of configuration 
files although the system community expressed that that would be highly
desirable~\cite{wang04automatic, zhang14encore, xu15systems}.
